|

### 2023-01-22 paper_comparison/paper_comparison/paper_comparison.Rmd
modify the different sigma plot

  # Combined with data for shape 1
  bind_rows(dat_shape_1) %>%
  VI_MODEL$plot() +
  facet_wrap(~shape, scales = "free", labeller = label_parsed, ncol = 4) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())
```

@@

# Generate and plot data for discrete uniform distribution
bind_rows(dat_dist_1, dat_dist_2, dat_dist_3, dat_dist_4) %>%
  VI_MODEL$plot() +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank()) +
  facet_wrap(~x_dist, ncol = 4, scales = "free")
```

@@

# Generate data for 300 observations
dat_n_300 <- poly_model(shape = 2, 
                        x = {
                          raw_x <- rand_uniform(-1, 1);
                          closed_form(~stand_dist(raw_x))
                        },
                        sigma = 1.5)$gen(300) %>%
  mutate(n = "N = 300")

# Generate data for other settings
map(c(50, 100), function(n) {
  poly_model(shape = 2, 
                   x = {
                     raw_x <- rand_uniform(-1, 1);
                     closed_form(~stand_dist(raw_x))
                     }, 
             sigma = 1.5)$
    gen(n, computed = select(dat_n_300[1:n, ], x, e)) %>%
    mutate(n = paste0("N = ", n))
}) %>%
  bind_rows(dat_n_300) %>%
  VI_MODEL$plot() +
  theme_light() +
  facet_wrap(~n, scales = "free", ncol = 3) +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())
```

@@

# Generate data for sigma 0.5
ori_dat <- poly_model(shape = 1, 
                      x = {
                        raw_x <- rand_uniform(-1, 1);
                        closed_form(~stand_dist(raw_x))
                        }, 
                      sigma = 0.5)$gen(300)

# Plot data for sigma 0.5
sp1 <- VI_MODEL$plot(ori_dat) + 
  ggtitle(quote(sigma~"="~0.5)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for sigma 1
sp2 <- poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 1)$
  gen(300, computed = select(ori_dat, x)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(sigma~"="~1)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for sigma 2
sp3 <- poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 2)$
  gen(300, computed = select(ori_dat, x)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(sigma~"="~2)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

# Generate and plot data for sigma 4
sp4 <- poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = 4)$
  gen(300, computed = select(ori_dat, x)) %>%
  VI_MODEL$plot() +
  ggtitle(quote(sigma~"="~4)) + 
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())

patchwork::wrap_plots(sp1, sp2, sp3, sp4, ncol = 4)
```

>>>>

  # Combined with data for shape 1
  bind_rows(dat_shape_1) %>%
  mutate(shape = factor(shape, levels = shape_labels)) %>%
  VI_MODEL$plot() +
  facet_wrap(~shape, scales = "free", labeller = label_parsed, ncol = 4) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())
```

@@

# Generate and plot data for discrete uniform distribution
bind_rows(dat_dist_1, dat_dist_2, dat_dist_3, dat_dist_4) %>%
  mutate(x_dist = factor(x_dist, 
                         levels = c("Uniform", 
                                    "Normal", 
                                    "Skewed", 
                                    "Discrete"))) %>%
  VI_MODEL$plot() +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank()) +
  facet_wrap(~x_dist, ncol = 4, scales = "free")
```

@@

# Generate data for 300 observations
dat_n_300 <- poly_model(shape = 2, 
                        x = {
                          raw_x <- rand_uniform(-1, 1);
                          closed_form(~stand_dist(raw_x))
                        },
                        sigma = 1.5)$gen(300) %>%
  mutate(n = "N: 300")

# Generate data for other settings
map(c(50, 100), function(n) {
  poly_model(shape = 2, 
                   x = {
                     raw_x <- rand_uniform(-1, 1);
                     closed_form(~stand_dist(raw_x))
                     }, 
             sigma = 1.5)$
    gen(n, computed = select(dat_n_300[1:n, ], x, e)) %>%
    mutate(n = paste0("N: ", n))
}) %>%

  # Combined with data for 300 observations
  bind_rows(dat_n_300) %>%
  mutate(n = factor(n, levels = c("N: 50", "N: 100", "N: 300"))) %>%
  VI_MODEL$plot() +
  theme_light() +
  facet_wrap(~n, scales = "free", ncol = 3) +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())
```

@@

# Generate data for sigma 0.5
dat_sigma_05 <- poly_model(shape = 1, 
                           x = {
                             raw_x <- rand_uniform(-1, 1);
                             closed_form(~stand_dist(raw_x))
                             }, 
                           sigma = 0.5)$gen(300) %>%
  mutate(sigma = "sigma: 0.5")

# Generate data for other sigma
map(c(1, 2, 4), function(sigma) {
  poly_model(shape = 1, 
                  x = {
                    raw_x <- rand_uniform(-1, 1); 
                    closed_form(~stand_dist(raw_x))
                    }, 
                  sigma = sigma)$
  gen(300, computed = select(dat_sigma_05, x)) %>%
  mutate(sigma = paste0("sigma: ", sigma))
}) %>%

  # Combined with data for sigma 0.5
  bind_rows(dat_sigma_05) %>%
  VI_MODEL$plot() + 
  facet_wrap(~sigma, ncol = 4, scales = "free", labeller = label_parsed) +
  theme_light() +
  xlab("Fitted values") +
  ylab("Residuals") +
  theme(axis.text = element_blank())
```
